Backpropagating Gravitational wave events

### 2022-05-07 src/ms.tex
Abstract improvements?

\begin{abstract}
Population synthesis simulation is the main workhorse for extracting physical information from a population of gravitational wave (GW) observations.
\kw{Unfortunately, it is difficult to follow current pathways for comparing simulations to observations when handling problems with a high dimensionality.}
\kb{I think we need to substantiate the previous sentence with citations that show this.}\kw{We do that in the introduction, is that enough? I reword the statement to be softer.}
In addition, it is very common to assume a set of assumptions, or "hyper-parameters", for how uncertain binary interactions proceed
for the entire population (often a fixed value), such as common envelope efficiency.
This limits the flexibility of the model and hence the potential to discover complex relations between hyper-parameters.
In this work, we introduce a new paradigm to extract physical information from GW observations.
We propose an inference pipeline to jointly infer the posterior density of both progenitor parameters (e.g. ZAMS masses) and hyper-parameters 
\kb{associated with uncertainties in binary evolution} \kw{I don't think we need this addition?} for each observation in GWTC3.
We showcase the effectiveness of this pipeline with GW150914, as well as its flexibility in studying a population of GW observations. 
\end{abstract}

>>>>

\begin{abstract}
One promising way to extract information about stellar astrophysics from
gravitational wave catalogs is to compare the catalog to the outputs of
population synthesis modeling with varying physical assumptions.  The parameter
space of physical assumptions in population synthesis is high-dimensional and
the choice of parameters that best represents the evolution of a binary system
may depend in an as-yet-to-be-determined way on the system's properties; indeed,
measuring the variation of population synthesis parameter settings with binary
properties is one of the principal ways to extract information about binary
astrophysics from catalogs. Here we propose an inference pipeline to
simultaneously infer the posterior density of stellar progenitor parameters
(e.g. zero-age main sequence masses) and population synthesis parameter settings
controlling modeled binary evolution from gravitational wave observations.  Our
pipeline can efficiently explore the high-dimensional space of population
synthesis settings and progenitor system properties for each system in a catalog
of gravitational wave observations.  We apply our pipeline to observations in
the third LIGO Virgo Kagra Gravitational Wave Transient Catalog (GWTC3).  We
showcase the effectiveness of this pipeline with a detailed study of the
progenitor properties and population synthesis settings that produce mergers
like the observed GW150914.
\end{abstract}
